# Data visualisation
<body id="start">
<div class="topnav">
  <a href='index.html#frontpage'>Front page</a>
  <a href='data-visualisation.html#data-visualisation'>Data visualisation</a>
  <a href='reproductibility.html#Reproductibility'>Reproductibility</a>
  <a href='sorting-directories.html#sorting-directories'>Directory structure</a>
  <a href='r-packages.html#R-packages'>R-package</a>
  <a href='sql.html#SQL'>SQL</a>
  <a href='cv.html#cv'>CV</a>
  <a href='plan-for-future.html#plan-for-future'>The future</a>
</div>
```{r setup_1, include=FALSE}
#Basic functions
library(tidyverse)
#Library to create dose-response curves
library(drc)
#Library to read excel documents
library(readxl)
#Library to use relative paths in coding instead of absolute paths
library(here)
#Library to create plots
library(ggplot2)
#Library for datatables
library(DT)
```
&nbsp;

To prove my skills in handling and making initial visualisations of data, a mock dataset supplied by J. louter (INT/ILC) has been analysed. This dataset was derived from an experiment in which adult _C.elegans_ were exposed to varying concentrations of different compounds. Then, after an exposure time of 68 hours, these _C.elegans_ were tested for amount of offspring they gave.  

Firstly, the data (which was stored in an Excel file) has been read using tidyverse's "readxl()". A datatable has been created to show this initial dataset
````{r reading_excelData}
excel_location<-here("data.raw/CE.LIQ.FLOW.062_Tidydata.xlsx")
Celegans_data_raw<-read_excel(excel_location, sheet = 1)
datatable(Celegans_data_raw, options = list(
  scrollX=TRUE
))
````

After reading in this data, it has been transformed in order to be able to create proper figures from it. For this, the important data columns have been selected:
expType: The type of experiment (Experimental, control)

RawData: Amount of offspring _C.elegans_ gave after 68 hours of exposure to the treatment

compName: The compound to which the _C.elegans_ was exposed to.

compConcentration: The concentration of the compound which the _C.elegans_ was exposed to.

````{r tidying_Excel}
#Dataset inspection and transformation

#Selecting data for this goal
Celegans_data_select<-Celegans_data_raw %>% dplyr::select(expType, compName, RawData, compConcentration)

#Datapoint 259 has a comma instead of a point. Transforming value via str_replace
Celegans_data_select$compConcentration<-Celegans_data_select$compConcentration %>% str_replace(",", ".")

#Now properly transforming the compConcentration data into numeric
Celegans_data_select$compConcentration<-Celegans_data_select$compConcentration %>% as.numeric()

#Transforming expType and compName into a factor variable

levels_exptype<-unique(Celegans_data_select$expType) #storing all exptype levels
Celegans_data_select$expType<-factor(Celegans_data_select$expType, levels = levels_exptype) #Transforming exptype
levels_compname<-unique(Celegans_data_select$compName) #Storing all compName levels
Celegans_data_select$compName<-factor(Celegans_data_select$compName, levels = levels_compname) #Transforming compName into factor

#Filtering NA's from RawData
Celegans_data_select<-Celegans_data_select %>% filter(!is.na(RawData))


#Re-loading the data
Celegans_data<-Celegans_data_select

#Checking if transformation went properly
datatable(Celegans_data, options = list(
  scrollX=TRUE
))
````

After tidying the data from the excel file, exploratory graphs have been created to study the data more thoroughly

````{r dataplots}
Celegans_data %>% ggplot(aes(x=log10(compConcentration+0.00005), y=RawData))+ #Added 0.0005 as otherwise, due to using log10, the S-medium values which are = 0, would be deleted.
  geom_jitter(aes(colour=compName, shape=expType), width = 0.05)+
  theme_bw()+
  labs(
    title="Effect of multiple treatments on offspring production by C.elegans",
    x="log 10 treatment concentration (nM)",
    y="Amount of offspring",
    colour="Treatment",
    shape="Experiment type"
  )
  
````

To properly be able to study the effect of the different treatments on _C.elegans_, the data will be normalized for the negative control S-medium.

````{r normalisingDataForNegativeControl}
#Determine the mean of the negative control
negctrl_mean<-Celegans_data_select$RawData[Celegans_data_select$expType=="controlNegative"] %>% mean()

#Normalising the data
Celegans_data_select_normalised<-Celegans_data_select %>% mutate(
  normalised_RawData_percentage=RawData/negctrl_mean*100
)

#Plotting the normalised data
Celegans_data_select_normalised %>% ggplot(aes(x=log10(compConcentration+0.00005), y=normalised_RawData_percentage))+
  geom_jitter(aes(colour=compName, shape=expType), width = 0.05)+
  theme_bw()+
  labs(
    title="Normalised effect of multiple treatments on offspring production by C.elegans",
    x="log 10 treatment concentration (nM)",
    y="Normalised amount of offspring (%)",
    colour="Treatment",
    shape="Experiment type"
  )

````

For a clearer picture of the correlations, a summarized version of the graph has also been made:
````{r ClearerGraph}
#Creating a summarised version of the data based on Treatment and concentration
Celegans_data_normalised_sum<-Celegans_data_select_normalised %>% filter(!is.na(normalised_RawData_percentage)) %>% group_by(compConcentration, compName) %>% summarise(
  mean_normalised=mean(normalised_RawData_percentage)
)

#Filtering out S-medium, as that is the negative control.
Celegans_data_normalised_sum<-Celegans_data_normalised_sum %>% filter(!compName=="S-medium")

#Plotting the summarised data.
Celegans_data_normalised_sum %>% ggplot(aes(x=log10(compConcentration+0.00005), y=mean_normalised))+
  geom_point(aes(colour=compName), size=3)+
  geom_line(aes(colour=compName))+
  theme_bw()+
  labs(
    title="Normalised effect of multiple treatments on offspring production by C.elegans",
    x="log 10 treatment concentration (nM)",
    y="Normalised amount of offspring (%)",
    colour="Treatment"
  )
````

Based on these exploratory graphs, we can conclude that 2,6-diisopropylnaphthalene, decane and nephthalene all cause a decrease in the ammount of offspring generated by C.elegans. Decane only appears to decrease offspring at higher concentrations, 2,6-diisopropylnaphthalene seems to cause a relatively constant decrease in offspring at increasing concentrations, and nephthalene seems to stagnate untill extremely high concentrations are used.

Based on this data, a LC-50 analysis could be performed.

</body>
