---
Title: "Test parameter"
output: html_document
params:
  country: "Netherlands"
  year: 2020
  month: 12
  month_end: FALSE
---

<body id="start">
<div class="topnav">
  <a href='index.html#Frontpage'>Frontpage</a>
  <a href='data-visualisation.html#data-visualisation'>Data visualisation</a>
  <a href='parametized-data.html#parametized-data'>Parametizing data</a>
  <a href='directory-structure.html#directory-structure'>Directory structure</a>
  <a href='creating-a-r-package.html#creating-a-r-package'>R-package</a>
  <a href='sql.html#SQL'>SQL</a>
  <a href='bibliography-using-zotero.html#Bibliography using Zotero'>Zotero</a>
  <a href='open-reproductibility-analysis.html#open-reproductibility-analysis'>Reproductibility</a>
  <a href='future-endeavours.html#future-endeavours'>Future endeavours</a>
  <a href='new-skills.html#New-skills'>New skills (Machine learning)<a/>
  <a href='cv.html#cv'>CV</a>
  <a href='bibliography.html#bibliography'>Bibliography</a>
</div>

# Parametized Data

To prove my skills in the producing parametized .Rmd's, I've used an online COVID-19 dataset and parametized the visualisation of this data file. For this parameterization, the country of the data, the year of the data and the months which the data covers have been added as variables.

For this page, the params have been set too:

- Country: "Germany" (Only shows data from the Germany)

- Year: 2020 (Only shows data from 2020)

- Month: 12 (Shows data from all 12 months of the year)

- Month_end: FALSE (Starts counting months from the start of the year (januari), if TRUE starts counting months from the end (december))

```{r}
library(here)
library(tidyverse)
library(ggplot2)
```

Parameter test 

```{r}
# Now integrating this into clean data
############################################################### Reading data
covid_data<-read.csv("./data.raw/data.csv")
covid_data_vis<-covid_data

############################################################### Mangling data
covid_years<-covid_data$year %>% unique()
covid_data_vis$year<-factor(as.character(covid_data$year), levels = as.character(covid_years)) #Making year a factor so it colours nicely instead of using a gradiant

months<-c("January", "Februari", "March", "April", "May", "June", "July", "August", "September", "October", "November", "December") #Storing months to plaster on x-axis

covid_data_filter1<-covid_data_vis %>% filter(countriesAndTerritories==params$country, #Filtering for countries and year
                                              year==params$year)

if (params$month_end) {
  covid_data_vis_filter2<-covid_data_filter1 %>% filter(month>=params$month)           #Filter for month based on if month_end is TRUE or FALSE
} else {
  covid_data_vis_filter2<-covid_data_filter1 %>% filter(month<=params$month)
}

############################################################### Creating visualisation: Cases per month
covid_data_vis_filter2 %>% group_by(month, year) %>% summarise(
  cases=mean(cases, na.rm=TRUE)
) %>% ggplot(aes(x=month, y=cases))+
  geom_point(aes(color=year))+
  geom_line(aes(group=year, color=year))+
  theme_bw()+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  labs(
    title=paste0("SARS-COV 2 cases in ",params$country, " per month in ", params$year),
    subtitle = "Data from ECDC",
    x="Month",
    y="COVID-19 cases",
    color="Year"
  )+
  scale_x_continuous(breaks=(seq(1:12)), labels = months)

############################################################# Creating visualisation: Deaths per month
covid_data_vis_filter2 %>% group_by(month, year) %>% summarise(
  deaths=mean(deaths, na.rm=TRUE)
) %>% ggplot(aes(x=month, y=deaths))+
  geom_point(aes(color=year))+
  geom_line(aes(group=year, color=year))+
  theme_bw()+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  labs(
    title=paste0("SARS-COV 2 deaths in ",params$country, " per month in ", params$year),
    subtitle = "Data from ECDC",
    x="Month",
    y="COVID-19 deaths",
    color="Year"
  )+
  scale_x_continuous(breaks=(seq(1:12)), labels = months)
```




