# Directory structure
<body id="start">
<div class="topnav">
  <a href='index.html#Frontpage'>Frontpage</a>
  <a href='data-visualisation.html#data-visualisation'>Data visualisation</a>
  <a href='parametized-data.html#parametized-data'>Parametizing data</a>
  <a href='directory-structure.html#directory-structure'>Directory structure</a>
  <a href='creating-a-r-package.html#creating-a-r-package'>R-package</a>
  <a href='sql.html#SQL'>SQL</a>
  <a href='bibliography-using-zotero.html#Bibliography using Zotero'>Zotero</a>
  <a href='open-reproductibility-analysis.html#open-reproductibility-analysis'>Reproductibility</a>
  <a href='future-endeavours.html#future-endeavours'>Future endeavours</a>
  <a href='new-skills.html#New-skills'>New skills (Machine learning)<a/>
  <a href='cv.html#cv'>CV</a>
  <a href='bibliography.html#bibliography'>Bibliography</a>
</div>>


&nbsp;

```{r setup_2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fs)
library(here)
```

To prove skills in the field off Guerilla Analytics folder structure, a previously unstructured file (named Daur2) has been re-sorted according to the Guerilla analytics principles. To showcase the file structure, the fs package command dir_tree will be performed

__Organised directory tree__
````{r DirTree_Organized}
fs::dir_tree(path = here("Daur2_Organisation_2.1/Daur2_Organized/"), type = "directory")

````

__Original directory tree__
````{r DirTree_Original}
fs::dir_tree(path = here("Daur2_Organisation_2.1/Daur2_Original/"), type = "directory")
````
