# Directory structure

<body id="start">
<div class="topnav">
  <a href='index.html#Frontpage'>Frontpage</a>
  <a href='data-visualisation.html#data-visualisation'>Data visualisation</a>
  <a href='parametized-data-germany.html#parametized-data'>Parametizing data</a>
  <a class="active" href='directory-structure.html#directory-structure'>Directory structure</a>
  <a href='creating-a-r-package.html#creating-a-r-package'>R-package</a>
  <a href='sql.html#SQL'>SQL</a>
  <a href='bibliography-using-zotero.html#Bibliography using Zotero'>Zotero</a>
  <a href='open-reproductibility-analysis.html#open-reproductibility-analysis'>Reproductibility</a>
  <a href='future-endeavours.html#future-endeavours'>Future endeavours</a>
  <a href='free-research-project-index.html#free-research-project'> Free research (Machine learning)</a>
  <a href='cv.html#cv'>CV</a>
  <a href='bibliography.html#bibliography'>Bibliography</a>
</div>



&nbsp;

```{r setup_2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fs)
library(here)
```

To prove skills in the field off Guerilla Analytics folder structure, a previously unstructured file (named Daur2) has been re-sorted according to the Guerilla analytics principles. To showcase the file structure, the fs package command dir_tree will be performed

Guerilla analytics folder structure gives a couple of guidelines to adhere too:

- create a separate folder for each analytics project

- Do not deeply nest folders

- Keep information about the data close to the data

- Store each dataset in its own sub-folder. 

- Do not change file names/move them

In my example below, you can see that in my original directory, there was no clear separate folder for each analytics project, with folders just being called "Formatieve_Opdracht1" (Translated: Formative Assignment 1) or "lesson 1-6". Furthermore, the original directories did not contain any form of structure in terms of .R / .RMD files, they were just scattered throughout the main directory. So, in the organised directories, every project has a separate R and RMD directory for these files.

__Organised directory tree__
````{r DirTree_Organized}
fs::dir_tree(path = here::here("Daur2_Organisation_2.1/Daur2_Organized/"), type = "directory")

````

__Original directory tree__
````{r DirTree_Original}
fs::dir_tree(path = here::here("Daur2_Organisation_2.1/Daur2_Original/"), type = "directory")
````
