# Directory structure
<body id="start">
<div class="topnav">
  <a href='index.html#frontpage'>Front page</a>
  <a href='data-visualisation.html#data-visualisation'>Data visualisation</a>
  <a href='sorting-directories.html#sorting-directories'>Directory structure</a>
  <a href='sql.html#SQL'>SQL</a>
  <a href='r-packages.html#R-packages'>R-package</a>
  <a href='bibliography-using-zotero.html#Bibliography using Zotero'>Zotero</a>
  <a href='reproductibility.html#Reproductibility'>Reproductibility</a>
  <a href='cv.html#cv'>CV</a>
  <a href='plan-for-future.html#plan-for-future'>The future</a>
</div>


&nbsp;

```{r setup_2, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(fs)
library(here)
```

To prove skills in the field off Guerilla Analytics folder structure, a previously unstructured file (named Daur2) has been re-sorted according to the Guerilla analytics principles. To showcase the file structure, the fs package command dir_tree will be performed

__Organised directory tree__
````{r DirTree_Organized}
fs::dir_tree(path = here("Daur2_Organisation_2.1/Daur2_Organized/"), type = "directory")

````

__Original directory tree__
````{r DirTree_Original}
fs::dir_tree(path = here("Daur2_Organisation_2.1/Daur2_Original/"), type = "directory")
````
