# SQL

<body id="start">
<div class="topnav">
  <a href='index.html#frontpage'>Front page</a>
  <a href='data-visualisation.html#data-visualisation'>Data visualisation</a>
  <a href='reproductibility.html#Reproductibility'>Reproductibility</a>
  <a href='sorting-directories.html#sorting-directories'>Directory structure</a>
  <a href='cv.html#cv'>CV</a>
  <a href='plan-for-future.html#plan-for-future'>The future</a>
  <a href='sql.html#SQL'>SQL</a>
</div>

In order to prove my skills in the field of data handling and SQL, this page will show me work with flu data, dengue data and the gapminder data from the {dslabs} package. The flu data and dengue data are both supplied by google, "www.google.org/flutrends AND www.google.org/denguetrends"

First of all, all datasets will be read and inspected in R

```{r dependencies_008, include=FALSE}
library(dslabs)
library(tidyverse)
```


```{r inspectingData}
#The gapminder dataset
gapminder %>% head()

dengue<-read.csv("./data/dengue_data.csv", skip = 10)
#The dengue dataset
dengue %>% head()

flu<-read.csv("./data/flu_data.csv", skip = 10)
#The flu dataset
flu %>% dplyr::select(Date:Japan) %>% head() #Selected till Japan for a cleaner table
```

