# Free space

```{r}
library(ggplot2)
library(tidyverse)

```


For my free Space, I will study [this site](https://towardsdatascience.com/recognition-and-counting-of-microorganisms-on-petri-dishes-53a499283dc8). in order to find information about using bacterial identification using machine learning. 

In this article, there is a link too the site [agar.neurosys.com](https://agar.neurosys.com/) which contains a dataset containing picture of agarplates in different conditions

Conclusion based on the site: this is _way_ too complicated to start out with. Trying to find a simpler introduction to machine learning, specifically in R

Trying [this link](https://www.datacamp.com/tutorial/machine-learning-in-r), mayhaps this'll give a better introduction.

Would appear that a technique called "KNN" might be a good algorythm to start with. Gonna follow the tutorial the previous link gives, using the "iris" dataset

First steps are too really undersand your data, and too visualise your data. So:

- Sepals are modified leaves which encase and protect the flower before it blooms

- Petals are modified leaves that surround the reproductive parts of the flower.

```{r}
iris %>% ggplot(aes(x=Sepal.Length, y=Sepal.Width, colour=Species))+
  geom_point()

iris %>% ggplot(aes(x=Petal.Length, y=Petal.Width, colour=Species))+
  geom_point()

str(iris)

table(iris$Species)

summary(iris)
```

