# R Packages

<body id="start">
<div class="topnav">
  <a href='index.html#frontpage'>Front page</a>
  <a href='data-visualisation.html#data-visualisation'>Data visualisation</a>
  <a href='reproductibility.html#Reproductibility'>Reproductibility</a>
  <a href='sorting-directories.html#sorting-directories'>Directory structure</a>
  <a href='cv.html#cv'>CV</a>
  <a href='plan-for-future.html#plan-for-future'>The future</a>
  <a href='sql.html#SQL'>SQL</a>
</div>

To prove my ability to create a package based on previous code, a set of functions will be created based on the "pokemon" dataset previously used will be created, and these functions will be transformed into a package.

First of, the pokemon package, supplied from "Rounak Banik" on [kaggle](https://www.kaggle.com/datasets/rounakbanik/pokemon), will be loaded in

```{r 009_dependancies}
library(tidyverse)
library(here)
library(ggplot2)
library(available)
```

```{r, eval=FALSE}
pokemon<-read_csv("data/pokemon.csv")

pokemon[1,] %>% select(name, type1, type2, abilities:is_legendary)


########## A Function which takes a list of pokemons, and gives you their type ######################################

pokemon_type<-function(...){
  arguments<-list(...) #Storing all arguments as a list
  for (x in arguments) #Making a command which repeats for all arguments in the list
  { if (is.na(pokemon$type2[pokemon$name==x])) #Determening whether the pokemon has 1 or 2 types, giving the appropriate message based on this
    print(paste0(pokemon$name[pokemon$name==x], " is a ", pokemon$type1[pokemon$name==x], " type"))
    else {
      print(paste0(pokemon$name[pokemon$name==x], " is a ", pokemon$type1[pokemon$name==x], " and a ", pokemon$type2[pokemon$name==x], " type"))
    }
  }
}


is.na(pokemon$type2[pokemon$name=="Chimchar"])

pokemon_type(pokemon, "Chimchar", "Drapion")

########## A Function which takes a name of 1 pokemon, and gives you a graph of their stat sheet. ######################

pokemon_stats<-function(pokemon_name){
  graph_data<-tidyr::pivot_longer(
    dplyr::select(
      pokemon[pokemon$name==pokemon_name,],
      hp, attack, defense, sp_attack, sp_defense, speed),
    cols=hp:speed, names_to = "stat", values_to = "value")

  graph_data$stat<-factor(graph_data$stat, levels = c("hp", "attack", "defense", "sp_attack", "sp_defense", "speed")) #Putting the stats in the proper porder

  ggplot2::ggplot(graph_data, ggplot2::aes(x=stat, y=value, fill=stat))+ #Visualising the separated stats
    ggplot2::geom_col(colour="black")+
    ggplot2::labs(title = paste0(pokemon_name,"'s stat breakdown"),
         x="",
         y="Stat value",
         fill="Stat")+
    ggplot2::theme_bw()
}

pokemon_stats(pokemon, "Drapion")

########## A function which takes a pokemon name, and states whether they're considered a legendary or not #################

pokemon_legendary<-function(pokemon_name){
  if (pokemon$is_legendary[pokemon$name==pokemon_name]==0){
    print(paste0(pokemon_name, " is not a legendary pokemon"))
  } else
  {
    print(paste0(pokemon_name, " is a legendary pokemon"))
  }
}

pokemon_legendary(pokemon, "Chimchar")

available(name = "PokemonAnalyse")


################ Function to determine a pokemon's weaknesses' #############################################3

pokemon_weakness_tidyverse<-function(pokemon_name){
  selected_pokemon<-pokemon[pokemon$name==pokemon_name,] %>% select(against_bug:against_water)
  
  types<-colnames(selected_pokemon) %>% substring(9)
  
  colnames(selected_pokemon)<-types
  
  selected_pokemon %>% pivot_longer(bug:water) %>% ggplot2::ggplot(ggplot2::aes(x=name, y=value, fill=name))+
    ggplot2::geom_col(color="black")+
    ggplot2::theme_bw()+
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle=45, hjust = 1), legend.position = "none")+
    ggplot2::scale_fill_manual(values = c("#82d132", "#2d282e", "#062b7a", "#cff71b", "#f731e4", "#a31738", "#e34009", "#95f0e2", "#43186e", "#18d945", "#ebce4d", "#a4f5ef", "#e8e8e8", "#7e18b5", "#e026af", "#d6cd85", "#8a8987", "#52abe3"))+
    ggplot2::labs(
      title = paste("Weakness' of", pokemon_name),
      x = "Type",
      y = "Damage multiplier"
    )
}

#Tidyverse way
pokemon_weakness<-function(pokemon_name){
  selected_pokemon<-dplyr::select(pokemon[pokemon$name==pokemon_name,], against_bug:against_water)
  
  types<-substring(colnames(selected_pokemon), 9)
  
  colnames(selected_pokemon)<-types
  
  final_pokemon<-tidyr::pivot_longer(selected_pokemon, bug:water)
  
  ggplot2::ggplot(final_pokemon, ggplot2::aes(x=name, y=value, fill=name))+
    ggplot2::geom_col(color="black")+
    ggplot2::theme_bw()+
    ggplot2::theme(axis.text.x = ggplot2::element_text(angle=45, hjust = 1), legend.position = "none")+
    ggplot2::scale_fill_manual(values = c("#82d132", "#2d282e", "#062b7a", "#cff71b", "#f731e4", "#a31738", "#e34009", "#95f0e2", "#43186e", "#18d945", "#ebce4d", "#a4f5ef", "#e8e8e8", "#7e18b5", "#e026af", "#d6cd85", "#8a8987", "#52abe3"))+
    ggplot2::labs(
      title = paste("Weakness' of", pokemon_name),
      x = "Type",
      y = "Damage multiplier"
    )
}

pokemon_weakness("Drapion")


```

