---
name: Pedro
surname: de Bos
position: "Student life sciences"
address: "University of applied sciences, Utrecht, Netherlands"
email: "pedrodebos@gmail.com"
github: PedroDeBos
linkedin: Pedro de Bos
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

````{r addingAnImage, out.width = "300px"}
knitr::include_graphics(
  path = "Dit_ben_ik_2.jpg"
)
````

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me
A driven 4th year life sciences student microbiology at the university of applied sciences of Utrecht, minoring in data sciences. Able too work in a ML1 microbiological laboratory working with bacteria, virusses and parasites. Have practical experience working sterile, performing PCR's and using equipment like the MALDI-TOF, BACTRON-6000. Also experienced in working with large data sets using bash, R, to order data, test for significance and create graphs.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bachelor life sciences", "2019-present", "University of applied sciences", "Utrecht, Netherlands",
  "High school diploma", "2014-2019", "Gerrit rietveld college", "Utrecht, Netherlands"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Nobel Prizes

```{r}
tribble(
  ~Year, ~Type, ~Desc,
  1903, "Physics", "Awarded for her work on radioactivity with Pierre Curie and Henri Becquerel",
  1911, "Chemistry", "Awarded for the discovery of radium and polonium"
) %>% 
  brief_entries(
    glue::glue("Nobel Prize in {Type}"),
    Year, 
    Desc
  )
```

# Publications

```{r}
library(dplyr)
knitr::write_bib(c("vitae", "tibble"), "packages.bib")

bibliography_entries("packages.bib") %>%
  arrange(desc(author$family), issued)
```

