---
name: Pedro
surname: de Bos
position: "Student life sciences"
address: "University of applied sciences, Utrecht, Netherlands"
email: "pedrodebos@gmail.com"
github: PedroDeBos
profilepic: "../../data/CV_Photo_2.jpg"
linkedin: Pedro de Bos
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# About me
A driven 4th year life sciences student microbiology at the university of applied sciences of Utrecht, minoring in data sciences. Able too work in a ML1 microbiological laboratory working with bacteria, virusses and parasites. Have practical experience working sterile, performing PCR's and using equipment like the MALDI-TOF, BACTRON-6000. Also experienced in working with large data sets using bash, R, to visualise data, work with high-troughput data, perform (sequencing) workflows

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Bachelor life sciences. Specialisation microbiology, minor data sciences", "2019-present", "University of applied sciences", "Utrecht, Netherlands",
  "High school diploma", "2014-2019", "Gerrit rietveld college", "Utrecht, Netherlands"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Languages 
```` {r}
library(tibble)
tribble(
  ~ Desc, ~ Language,
  "Mother language, fluent in both speaking and writing", "Dutch [x][x][x][x][x]",
  "Learned language, fluent in writing, proficient in speaking", "English [x][x][x][x][.]",
  "Comfortable with visualising data, performing statistics, writing functions, simple workflows (RNAseq, metagenomics). Portfolio is available on pedrodebos.github.io", "R [x][x][x][.][.]",
  "Comfortable with writing small scripts for importing data, for-do-done loops, functions containing if/then statements", "bash [x][x][x][.][.]"
) %>%
  detailed_entries(Desc, , Language, )
````

# Skills

```{r}
tribble(
  ~Skill, ~Explanation,
  "Group projects", "8 Years of experience in 3-6 month long group projects",
  "Team communication", "Comfortable using teams, github, messenger apps for communication.",
  "Learning new programs", "Learned how to use the basics of bash, R within 10 weeks."
) %>%
  detailed_entries(Explanation, , Skill, )
```


